% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{hyperref}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}
\name{Johannes Mauritzen}

\address{mob:  +47 90 56 64 62 \\ email: johannes.mauritzen@bi.no \\
website:  \url{jmaurit.github.io}}

\section{Personal}
\begin{itemize}
\item[] Born July 21, 1982
\item[] Norwegian Citizen
\end{itemize}

\section{PUBLICATIONS}

\normalsize{\section{Peer Reviewed}}
\begin{itemize}
\setlength{\itemsep}{10pt}

\item[] \emph{Are solar panels commodities? A Bayesian hierarchical approach to detecting quality differences and asymmetric information}\\
European Journal of Operational Research\\
Volume 280, Issue 1, January 2020, Pages 365-382.

\item[] \emph{Real-time Versus Day-ahead Market Power in a Hydro-based Electricity Market} \\
With Thomas Tanger\aa s \\
Journal of Industrial Economics\\
Volume 66, Issue 4, June 2019

\item[] \emph{The Other Renewable: Hydropower Upgrades and Renewable Portfolio Standards} \\
With Stein-Erik Fleten and Carl Ulrich.\\
The Energy Journal, Vol. 39, No. 2. 2018.

\item[] \emph{Cost, Contractors and Scale: An Empirical Analysis of the California Solar Market}  \\
The Energy Journal, Vol. 38, No. 6. 2017.

\item[] \emph{The Effect of Oil Prices on Field Production: Evidence from the Norwegian Continental Shelf}\\
Oxford Bulletin of Economics and Statistics, Volume 79, Issue 1, February 2017, pages 124-144.

\item[] \emph{How electricity price spikes can help overcome the energy efficiency gap}\\
Economics Letters, Vol. 134, September 2015, Pages 114-117.

\item[] \emph{Now or Later? Trading wind power closer to real-time and how poorly designed subsidies lead to higher balancing costs}\\
The Energy Journal, Vol. 36, No. 4, 2015

\item[] \emph{The Decision to Scrap a Wind Turbine: Policy changes, scrapping incentives and why wind turbines in good locations get scrapped first}\\
The Energy Journal, Vol. 35, No. 2, 2014.

\item[] \emph{Dead Battery? Wind Power, the Spot Market, and Hydropower Interaction in the Nordic Electricity Market}\\
The Energy Journal, Vol. 34, No. 1, 2013
\end{itemize}

\normalsize{\section{Conference Proceedings}}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] \emph{What Happens When it's Windy in Denmark? How Wind Power Affects Price Variability in the Nordic Electricity Market}\\
IAEE International Conference, Stockholm, June 2011  \\
Student Paper Award Recipient

\item[] \emph {Sun and Lemons: Getting over Information Asymmetries in the California Solar Market} \\
Allied Social Sciences Associations Conference in Boston, January 2015

\end{itemize}


\normalsize{\section{Working Papers}}
\begin{itemize}
\setlength{\itemsep}{10pt}

\item[] \emph{Aggregating or diversifying risk? Tail correlations, transmission flows and prices across wind power areas.} With Genaro Sucarrat, BI.
\item[] \emph{The auditor, asymmetric information and dividend payout in small private firms: Evidence from a natural experiment.} With Hakim Lyngstadås, BI.
\item[] \emph{The effect of wind power investments on rural labor markets.}

\end{itemize}

\section{REPORTS AND ANALYSIS}
\begin{itemize}
\setlength{\itemsep}{5pt}
\item[] \href{http://klimastiftelsen.no/wp-content/uploads/2015/06/NK5_2015_Solenergirevolusjonen.pdf}{\emph{En verden med billig solkraft} Hva betyr solenergirevolusjonen, Norsk Klimastiftelsen nr 5/2015}
\end{itemize}

\section{PUBLICATIONS IN POPULAR PRESS}
\begin{itemize}
\setlength{\itemsep}{5pt}

\item[] \emph{Norway cannot pretend climate goals do not exist}, Financial Times, letters, March 18th, 2019

\item[] \emph{Minnesota Vikings}, The Economist, letters, January 17th, 2019

\item[] \emph{Look to the likes of GE for sign of the next downturn}, The Financial Times, letters, November 29th, 2018

\item[] \href{https://www.economist.com/news/letters/21719426-liberia-charles-murray-france-turkey-electric-cars-dead-words-letters-editor}{\emph{Car trouble.} The Economist, letters, March 25th, 2017}

\item[] \href{https://next.ft.com/content/a9ca4ad4-15d8-11e6-9d98-00386a18e39d}{\emph{Nothing paradoxical about Norwegian policies.} Financial Times, letters, May 10th, 2016}

\item[] \href{http://www.economist.com/news/letters/21676738-letters}{\emph{The Norwegian model.} The Economist, letters, October 24th, 2015}

\item[] \href{http://www.ft.com/intl/cms/s/0/e22cba5c-1bfa-11e5-a130-2e7db721f996.html#axzz3giRBkRau}{\emph{An outdated view of wind turbines.}} Financial Times, letters, July 3rd, 2015.

\item[] \href{http://www.ft.com/intl/cms/s/0/313360bc-a00c-11e4-aa89-00144feab7de.html#axzz3PVKMfhY5}{\emph{The attractiveness of electric cars has little to do with the price of oil.}} Financial Times, letters, January 21st, 2015.

\item[] \href{http://www.economist.com/news/letters/21595871-livestock-and-emissions-california-technology-and-jobs-algorithms}{\emph{Technology, jobs and urbanisation.}}   The Economist, letters, February 8th, 2014.

\item[] \href{http://www.economist.com/news/letters/21571848-nordic-countries-private-schools-immigration-sandhurst-ed-koch-richard-iii}{\emph{Too generous to Norway.}} The Economist, letters, February 16th, 2013.

\item[] \href{http://www.ft.com/intl/cms/s/0/26168da6-238d-11e2-bb86-00144feabdc0.html#axzz2sclP2DP5}{\emph{Electric cars are being mass-produced.}}  Financial Times, letters, November 5th, 2012.

\item[] \href{http://www.ft.com/intl/cms/s/0/553d8cf6-fb56-11e1-87ae-00144feabdc0.html#axzz2sclP2DP5}{\emph{Europe should let China subsidize its energy production.}}  Financial Times, Letters, September 11th, 2012.


\normalsize{\section{In Norwegian}}

\item[] \emph{Koronaviruset gir et varsko for norsk økonomi.} Dagens Næringsliv, February 29th, 2020
}

\item[] \emph{Vindkraft er s\ae rlig gunstig i Norge.} Adresseavisen, March 22nd, 2018.

\item[]  \href{http://sysla.no/meninger/stromkabler-til-europa-vil-vaere-bra-norge/}{\emph{Str\o mkabler til Europa vil være bra for Norge.}} Sysla, May 8th, 2017.

\item[] \href{http://www.adressa.no/meninger/ordetfritt/2017/03/01/Midtbyen-burde-bli-mer-som-et-shoppingsenter-14344490.ece?cx_Deling=AddThis}{\emph{Midtbyen burde bli mer som et shoppingsenter.}} Adresseavisen, March 1st, 2017.

\item[] \href{http://www.e-pages.dk/adresseavisen/5350/article/525164/33/6/render/?token=d6dbc5eb6e27835a4e2c9e1c460302d6}{\emph{Powerhouse er den type grep som byen trenger}} Adresseavisen, January 18th, 2017

\item[] \href{http://syslagronn.no/2016/05/12/syslagronn/serieproduksjon-skaper-energirevolusjon_87844/.VzQ1IfhgWKc.twitter}{\emph{Serieproduksjon skaper energirevelosjon.}} Sysla, May 10th, 2016

\item[] \href{http://www.e-pages.dk/adresseavisen/5117/article/411985/41/6/render/?token=21b06b63e6a1cbd3e62966cf5706d3ab}{\emph{Str\o mkundene slipper \r{a} «bl\o».}} Adresseavisen, April 20th, 2016.
\item[] \href{http://syslagronn.no/2016/02/12/syslagronn/derfor-fant-republikanerne-og-demokratene-sammen_76977/}{\emph{Derfor fant republikanerne og demokratene sammen.}} Sysla, February 12th, 2016.
\item[] \href{http://www.syslagronn.no/2015/12/01/syslagronn/byen-er-redskapet-for-a-bekjempe-klimaendringer_67934/}{\emph{Byen er redskapet for å bekjempe klimaendring.}} Sysla, December 1st, 2015.
\item[] \href{http://www.dn.no/meninger/2015/09/20/2043/Politikk/god-samfunnskonomi-fra-mdg}{\emph{God samfunnsøkonomi fra MDG.} Dagens n\ae ringsliv, September 21st, 2015.}
\item[] \href{http://www.syslagronn.no/2015/08/20/syslagronn/derfor-blir-solenergi-billigere_51484/}{\emph{Derfor blir solenergi billigere.} Sysla, August 20th, 2015.}
\item[] \href{http://www.e-pages.dk/bergenstidende/1809/article/264899/28/2/render/?token=02cd272aa0579373983f0bf8c4cee611}{ \emph{K\o prising skal gjøre vondt}} Bergens Tidende, April 27th 2015
\item[] \href{http://www.bt.no/meninger/debatt/Derfor-faller-oljeprisen-3282375.html}{ \emph {Derfor faller oljeprisen} Bergens Tidende, January 19th, 2015}
\item[] \href{http://www.e-pages.dk/bergenstidende/1700/article/227941/31/4/render/?token=5207fb9bf5f917b5276532ef05164266}{ \emph {Billig Klimaforsikring} Bergens Tidende, January 6th, 2015}
\item[] \href{http://www.bt.no/meninger/debatt/Mytene-om-hoye-bygg-3234980.html}{ \emph {Mytene om h\o ye bygg} Bergens Tidende, November 6th, 2014}
\item[] \href{http://www.bt.no/meninger/debatt/Den-absurde-skattepolitikken-3191273.html}{\emph{Den absurde skattepolitikken} Bergens Tidende, September 8th, 2014}
\item[] \emph {Sykkelpartiet H\o yre}  Bergens Tidende, August 4th, 2014.
\item[] \emph {Dyr symbolpolitikk}  Bergens Tidende, June 7th, 2014.
\item[] \emph {En lysere sykkelfremtid}  Bergens Tidende, May 7th, 2014.
\item[] \emph {Rene investerings}  Bergens Tidende, April 5th, 2014.
\item[] \href{http://www.nhh.no/Files/Filer/institutter/for/bedriftsøkonomisk_debatt/2013/mauritzen-livet_etter_oljen-bt-310713.pdf}{\emph {Livet etter oljen}  Bergens Tidende, July 31st, 2013.}
\item[] \emph {Bevar Bryggen, Bygg Bybanen}  Bergens Tidende, March 30th, 2013.
\item[] \emph {Norge er sykkelversting i Nord-Europa} Aftenposten, September 20th, 2012.
\item[] \emph {Bygg H\o yere!, Aftenposten} August 10th, 2012.
\end{itemize}

% \section{PRESENTATIONS}

%\begin{itemize}
%\normalsize{\section{2016}}
%\item[] IAEE Bergen, Real Options Conference Oslo, Nordic Industrial Organisation Meeting Reykjavik.

%\normalsize{\section{2015}}
%\item[] ASSA Boston, Ume\r{a} School of Business and economics, FIBE, UCL Department of Statistics, NTNU Department of Industrial Economics, University of Stavanger Business School, University of Aberdeen, RWTH Aachen.
%\normalsize{\section{2014}}
%\item[] IAEE New York, IAEE Asia Conference - Beijing, Research Institute of Industrial Economics (Stockholm), Norwegian Conference for Business Economics (FIBE),Workshop on Intermittent Renewables and Market Design - Hardanger, Economics of Uncertainty Workshop - NTNU, CenSES Annual Conference, University of Neuchatel
%\normalsize{\section{2013}}
%\item[] IAEE Dusseldorf, Research Institute of Industrial Economics, FIBE, CenSES Annual Conference
%\normalsize{\section{2012}}
%\item[] NTNU Department of Industrial Economics, University of Southern Denmark - Esbjerg, Swedish Department of Commerce - Energy Division
%\end{itemize}


\section{RESEARCH AND WORK EXPERIENCE}
					    % is 3 inches wide
                  \begin{itemize}
                  \setlength{\itemsep}{10pt}
                  \item[] Associate Professor, Department of Accounting, Auditing and Business Analytics, BI Norwegian Business School. Campus Trondheim \\ March 2016 -
                  \item[] Adjunct Associate Professor, Department of Business and Management Science, NHH Norwegian School of Economics, Bergen, Norway \\ January 2020 -
                  \item[] Post-doctoral Fellow, Department of Industrial Economics and Technology Management, Norwegian University of Science and Technology. \\ January 2016 - February 2016.
                  \item[] Post-doctoral Fellow, Center for Sustainable Energy Studies, Norwegian School of Economics, Department of Business and Management Science. \\ January 2013 - December 2015.

                  \item[] Visiting researcher, Department of Statistical Science, University College London. \\ February - March, 2015

                  \item[] Research Institute of Industrial Economics (IFN), Stockholm, Sweden.
                    \begin{itemize}
                    \item[] Affiliated Researcher, January 2013 to January 2016.
                    \item[] Research Fellow, May 2012 to December 2012.
                    \item[] Guest Researcher, September to 2011 to May 2012.
                    \end{itemize}
                  \item[] Research Scholar, NHH Norwegian School of Economics, Department of Finance and Management Science. August 2008 to August 2012.

                  \item[] Graduate Research Assistant, Center for Reinventing Public Education, University of Washington, Seattle, WA. June 2007 to August 2008.

                  \item[] Research Analyst, Levy Forecasting Center, LLC, Mount Kisco, NY. July 2004 to June 2006.

                  \end{itemize}

\section{TEACHING}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Lecturer and course responsible, Energy Industry Analytics, NHH, Spring 2020.
\item[] Advisor, Bachelor Thesis in Macroeconomics, BI, Spring 2017-2019.
\item[] Advisor, Bachelor Thesis in Business Economics, BI, Spring 2019.
\item[] Lecturer, Business Economics, BI, Fall 2016.
\item[] Lecturer, Applied Macroeconomics, BI, Fall 2016-2019.
\item[] Lecturer, Microeconomics (with Ruud Egging), NTNU.  Fall 2015.
\item[] Investment Science (part of course Project Management), NTNU.  Fall 2015.
\item[] Lecturer, Bergen Summer Research School, University of Bergen.  Getting started with energy and climate data analysis with R.  Summer 2014.
\item[] Lecturer, Physics and Economics of Renewable Energy (with Jan Petter Hansen, University of Bergen), NHH.  Spring 2010 and spring 2011.
\item[] Teaching Assistant: Driftsregnskap og Budsjettering (Introduction to Management Accounting and Budgeting.)
\item[] Teaching Assistant: Introduction to Microeconomics, Introduction to Macroeconomics.  University of Washington, Department of Economics. Fall 2006, Spring 2007.
\item[] Norwegian Instructor, high school credit course.  Concordia Language Villages, Bemidji MN.  Summer 2006.
\item [] Masters thesis supervision, NHH (9 Thesis):
  %\begin{itemize}
  %\item[] Emma Micklem, NHH. \emph{Wind Power in South Africa.}
  %\item[] Christopher Brenner, NHH. \emph{Biomass and the German Energy Policy.}
  %\item[] Louis Magnus Pauchon, NHH. \emph{Energy Efficiency Policy for Buildings: A comparison of Norway and France.}
  %\item[] Arild Huitfeldt og Torgeir Persen, NHH.  \emph{Realopsjonsanalyse av Vindkraftverk under utvikling – Vil en realopsjonstiln\ae rming forbedre verdivurderingen av et vindkraftverk under utvikling? (Will a Real-Options Approach Improve the Valuation of a Wind Park under Development?)}
  %\item[] Kjartan Skj\ae veland and T\o nnes Thompson, NHH. \emph{The End of a Long Term Relationship between the Price of Crude Oil and Natural Gas: A Cointegration Approach.}
  %\item[] Arve Tundal and Mari Hougsn\ae s, NHH.  \emph{Kostnadsanalyse: Hydro Aluminium Sunndal.  En vurdering av fremtidig anodeleverand\o r til Hydro Aluminium Sunndal. (A Valuation of Future Anode Deliveries to Hydro Aluminium Sunndal.)}
  %\item[] Nikolaos Tsagkaropoulos, NHH. \emph{Bicycle Sharing Systems, Are They Here To Stay?} Fall 2014
  %\item[] Ivan Paladin and Kenza Taoufik, NHH. \emph{The Cost of Sun: The Case Study of Croatia using a Levelized Cost of Energy Approach.}
  %\item[] Sven Arensman, NHH. \emph{A Bright New Day for Thermal Energy Storage in CSP.}
  %\end{itemize}
\end{itemize}

\section{Education}

\begin{itemize}
\normalsize{\section{Ph.D. Management Science \\ August 2008 - May 2012}}
\item[] Department of Finance and Management Science\\
NHH Norwegian School of Economics \\
Bergen, Norway \\

\normalsize{\section{\bf Master of Arts \\ August 2006 - June 2008}}
\item[] Department of Economics \\
University of Washington \\
Seattle, WA, USA \\

\normalsize{\section{\bf Bachelor of Arts \\ August 2000 - May 2004}}
\item[] St. Olaf College  \\
Mathematics and History Majors \\
Summe Cum Laude \\
Northfield, MN, USA \\
\end{itemize}

%\section{REFEREEING}
%\begin{itemize}
%\item[] Journal of Environmental Economics and Management, The Energy Journal, Energy Economics, Journal of Energy Engineering, Journal of Sustainable Energy Planning and Management
% \end{itemize}

\section{Programming}
\begin{itemize}
  \item[] R, Python, html/css, Stata, some Matlab, C++
\end{itemize}

\section{Pedagogical training}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Teaching Economics, credit course, Fall 2006, Department of Economics, University of Washington, Seattle (with Eugene Silberberg)

\item[] Pedagogical Training Certificate, Spring 2013, NHH, (with Arild Raaheim, University of Bergen/NHH)
\end{itemize}

\end{document}
