% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
\usepackage{hyperref}

%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\topmargin=-0.5in  % start text higher on the page
\setlength{\textheight}{10in} % increase text height to fit resume on 1 page
\begin{document}
\name{Johannes Mauritzen}

\address{mob:  +47 90 56 64 62 \\ email: johannes.mauritzen@bi.no \\
website:  \url{jmaurit.github.io}}


\begin{resume}
\section{PERSONAL}
\begin{itemize}
\item[] Born July 21, 1982
\item[] Norwegian Citizen

\normalsize{\section{Languages}}
\item[] Norwegian and English: Native
\item[] German: Beginner

\normalsize{\section{Fields of interest}}
\item[] Energy Economics, Business Economics, Empirical Finance, Natural Resource and Environmental Economics, Applied Statistics/Econometrics, Industrial Organisation
\end{itemize}


\section{PUBLICATIONS}

\normalsize{\section{Peer Reviewed}}
\begin{itemize}
\setlength{\itemsep}{10pt}

\item[] \emph{The Other Renewable: Hydropower Upgrades and Renewable Portfolio Standards. With Stein-Erik Fleten and Carl Ulrich. The Energy Journal, Vol. 39, No. 2}

\item[] \emph{Cost, Contractors and Scale: An Empirical Analysis of the California Solar Market}  \\
The Energy Journal, Vol. 38, No. 6.

\item[] \emph{The Effect of Oil Prices on Field Production: Evidence from the Norwegian Continental Shelf}\\
Oxford Bulletin of Economics and Statistics, Volume 79, Issue 1, February 2017, pages 124-144.

\item[] \emph{How electricity price spikes can help overcome the energy efficiency gap}\\
Economics Letters, Vol. 134, September 2015, Pages 114-117.

\item[] \emph{Now or Later? Trading wind power closer to real-time and how poorly designed subsidies lead to higher balancing costs}\\
The Energy Journal, Vol. 36, No. 4, 2015

\item[] \emph{The Decision to Scrap a Wind Turbine: Policy changes, scrapping incentives and why wind turbines in good locations get scrapped first}\\
The Energy Journal, Vol. 35, No. 2, 2014.

\item[] \emph{Dead Battery? Wind Power, the Spot Market, and Hydropower Interaction in the Nordic Electricity Market}\\
The Energy Journal, Vol. 34, No. 1, 2013
\end{itemize}

\normalsize{\section{Conference Proceedings}}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] \emph{What Happens When it's Windy in Denmark? How Wind Power Affects Price Variability in the Nordic Electricity Market}\\
IAEE International Conference, Stockholm, June 2011  \\
Student Paper Award Recipient

\item[] \emph {Sun and Lemons: Getting over Information Asymmetries in the California Solar Market} \\
Allied Social Sciences Associations Conference in Boston, January 2015

\item[] \emph{Real-time Versus Day-ahead Market Power in a Hydro-based Electricity Market} \\
With Thomas Tanger\aa s \\
IAEE International Conference, Antalya, May 2015

\item[] \emph{Lease or Buy? A Bayesian model of quality differences in California solar panels}\\
Conference Proceedings, IAEE International Conference, Bergen, June 2016
\end{itemize}


\section{REPORTS AND ANALYSIS}
\begin{itemize}
\setlength{\itemsep}{5pt}
\item[] \href{http://klimastiftelsen.no/wp-content/uploads/2015/06/NK5_2015_Solenergirevolusjonen.pdf}{\emph{En verden med billig solkraft} Hva betyr solenergirevolusjonen, Norsk Klimastiftelsen nr 5/2015}
\end{itemize}

\section{RESEARCH AND WORK EXPERIENCE}
					    % is 3 inches wide
                  \begin{itemize}
                  \setlength{\itemsep}{10pt}
                  \item[] Associate Professor, Department of Accounting, Auditing and Business Analytics, BI Norwegian Business School. Campus Trondheim \\ March 2016 -
                  \item[] Adjunct Associate Professor, Department of Business and Management Science, NHH Norwegian School of Economics, Bergen, Norway \\ January 2020 -
                  \item[] Post-doctoral Fellow, Department of Industrial Economics and Technology Management, Norwegian University of Science and Technology. \\ January 2016 - February 2016.
                  \item[] Post-doctoral Fellow, Center for Sustainable Energy Studies, Norwegian School of Economics, Department of Business and Management Science. \\ January 2013 - December 2015.
                  \item[] Visiting researcher, Department of Statistical Science, University College London. \\ February - March, 2015
                  \item[] Research Institute of Industrial Economics (IFN), Stockholm, Sweden.
                    \begin{itemize}
                    \item[] Affiliated Researcher, January 2013 to present.
                    \item[] Research Fellow, May 2012 to December 2012.
                    \item[] Guest Researcher, September to 2011 to May 2012.
                    \end{itemize}
                  \item[] Research Scholar, NHH Norwegian School of Economics, Department of Finance and Management Science. August 2008 to August 2012.
                  Research towards Ph.D. degree.
                  \item[] Graduate Research Assistant, Center for Reinventing Public Education, University of Washington, Seattle, WA. June 2007 to August 2008.
                  \item[] Research Analyst, Levy Forecasting Center, LLC, Mount Kisco, NY. July 2004 to June 2006.
                  \end{itemize}

\section{TEACHING}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Lecturer and course responsible, Energy Industry Analytics, NHH, Spring 2020.
\item[] Advisor, Bachelor Thesis in Macroeconomics, BI, Spring 2017, 2018.
\item[] Lecturer, Business Economics, BI, Fall 2016.
\item[] Lecturer, Applied Macroeconomics, BI, Fall 2016, 2017.
\item[] Lecturer, Microeconomics (with Ruud Egging), NTNU.  Fall 2015.
\item[] Investment Science (part of course Project Management), NTNU.  Fall 2015.
\item[] Lecturer, Bergen Summer Research School, University of Bergen.  Getting started with energy and climate data analysis with R.  Summer 2014.
\item[] Guest Lecturer, Environmental Economics, NHH.  Non-market valuation and using the R statistical programming language.  Spring 2013 and spring 2014.
\item[] Lecturer, Physics and Economics of Renewable Energy (with Jan Petter Hansen, University of Bergen), NHH.  Spring 2010 and spring 2011.
\item[] Teaching Assistant: Driftsregnskap og Budsjettering (Introduction to Management Accounting and Budgeting.)
\item[] Teaching Assistant: Introduction to Microeconomics, Introduction to Macroeconomics.  University of Washington, Department of Economics. Fall 2006, Spring 2007.
\item[] Norwegian Instructor, high school credit course.  Concordia Language Villages, Bemidji MN.  Summer 2006.
\end{itemize}

\section{EDUCATION}

\begin{itemize}
\normalsize{\section{Ph.D. Business Economics \\ August 2008 - May 2012}}
\item[] Department of Finance and Management Science\\
NHH Norwegian School of Economics \\
Bergen, Norway \\

\normalsize{\section{\bf Master of Arts \\ August 2006 - June 2008}}
\item[] Department of Economics \\
University of Washington \\
Seattle, WA, USA \\

\normalsize{\section{\bf Bachelor of Arts \\ August 2000 - May 2004}}
\item[] St. Olaf College  \\
Mathematics and History Majors \\
Summe Cum Laude \\
Northfield, MN, USA \\
\end{itemize}

\section{PROGRAMMING}
\begin{itemize}
  \item[] R, Python, html/css, Stata, some Matlab, C++, Visual Basic
\end{itemize}

\section{PEDAGOGICAL TRAINING}
\begin{itemize}
\setlength{\itemsep}{10pt}
\item[] Teaching Economics, credit course, Fall 2006, Department of Economics, University of Washington, Seattle (with Eugene Silberberg)

\item[] Pedagogical Training Certificate, Spring 2013, NHH, (with Arild Raaheim, University of Bergen/NHH)
\end{itemize}



\end{resume}
\end{document}
